On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-09-10 Manuscript/manuscript.tex
removed resolved

\paragraph{Bias-Corrected (BC) CI}
The procedure for constructing a bias-corrected Bootstrap CI based on standard
bootstrap is described in \citet{carpenter2000bootstrap}. Let
$\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
$b \in \{1, \ldots, B\}$. Define 
$\alpha_1 = \Phi(2\hat{z}_0 - z_{1 - \alpha/2})$ 
and $\alpha_2 = \Phi(2\hat{z}_0 - z_{\alpha/2})$. 
A $(1 - \alpha)100\%$ ~BC CI is
\[
(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
\]
\eds{the $z_{\alpha/2}$ and $z_{1 - \alpha/2}$ may need to be switched now in 
$\alpha_1$ and $\alpha_2$ with the quantile definition for $z_{\alpha}$ -- 
please check.} 
\mc{yes they had to be switched}

\paragraph{Bias-Corrected and Accelerated (BCA) CI}
The BCA CI was first suggested in \citet{efron1987better}. Let $Z_{(i)}$ be the 
original sample without the $i$th block $z_i$ for $i \in \{1, \ldots, k\}$, let 
$\hat{\theta}_{(i)}$ be the statistic of $Z_{(i)}$, and let 
$\hat{\theta}_{(.)} = k^{-1}\sum_{i=1}^{k} \hat{\theta}_{(i)}$. 
Let
\begin{equation*}
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}.
\end{equation*}
Define
\begin{equation*}
\alpha_1 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{\alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{\alpha/2})}\right)
\end{equation*}
and
\begin{equation*}
\alpha_2 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{1 - \alpha/2})}\right).
\end{equation*}
\eds{please check $z_{\alpha/2}$ and $z_{1 - \alpha/2}$ in 
$\alpha_1$ and $\alpha_2$ with the quantile definition for $z_{\alpha}$} 
\mc{this one is okay}
A $(1 - \alpha)100\%$ ~BCA CI is
\[
(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
\]
This CI is not necessarily centered by $\hat\theta_n$. The BCA method corrects 
for bias and skewness of the $B$ bootstrap point estimates 
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including 
bias-correction and acceleration factors. The acceleration factor refers to the 
rate of change of the standard error of $\hat\theta_n$ with respect to $\theta$.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_sigma}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal standard deviation $\sigma_w$ \eds{$\sigma_w$?} \mc{addressed}
    of a stationary series with 
    marginal unit exponential distribution obtained by transforming an AR(1) process
    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_sigma}
\end{figure}

@@

The empirical coverage rates for $\mu$, $\sigma_w$, \eds{define $\sigma_w$} 
\mc{added definitions for $\mu$ and $\sigma_w$ in the above paragraph} and 
the lag-1 autocorrelation coefficient \mc{replaced $\phi$ here, as I understand
it, we are not using $\phi$ in reference to the temporal dependence of the 
exponentially distributed series?}, as well as 95\%
confidence intervals of the real coverage are displayed in 
\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_phi}}. 
Additionally, a set of 50 CIs are displayed for each of the percentile, 
BC, and recentered percentile approaches for exponentially distributed
samples of $n \in \{800, 1600\}$ with lag-1 autocorrelation coefficient 0.355
($\phi = 0.4$) in Figure~\ref{fig:eri}.

It appears that a greater sample size is generally required for the bootstrap
CIs to cover the mean and standard deviation parameters in the exponential
margin case than in the normal margin case. However, the trends and patterns
discussed in the main text regarding the performance of various methods and
diverse parameters remain consistent. For example, Student's $t$ confidence
intervals still exhibit higher coverage rates in comparison to alternative
methods. Performance continues to be more favorable when temporal dependence is
negative rather than positive. Of particular significance, the percentile, BC,
and BCA confidence intervals still display a decline in coverage accuracy for
the lag-1 autocorrelation coefficient as sample size increases as demonstrated
in Figure~\ref{fig:eri}. Both the percentile and BC intervals persist in
manifesting the same bias issue. On the other hand, the recentered percentile
confidence interval continues to be effective in estimating the temporal 
dependence \mc{replaced $\phi$ again here} due to the
inherent unbiasedness of the original point estimator. In sum, the findings for
series that are marginally exponentially distributed closely mirror those
attained for series that are marginally normally distributed.

>>>>

\paragraph{Bias-Corrected (BC) CI}
The procedure for constructing a bias-corrected Bootstrap CI based on standard
bootstrap is described in \citet{carpenter2000bootstrap}. Let
$\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for
$b \in \{1, \ldots, B\}$. Define 
$\alpha_1 = \Phi(2\hat{z}_0 - z_{1 - \alpha/2})$ 
and $\alpha_2 = \Phi(2\hat{z}_0 - z_{\alpha/2})$. 
A $(1 - \alpha)100\%$ ~BC CI is
\[
(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
\]
%\eds{the $z_{\alpha/2}$ and $z_{1 - \alpha/2}$ may need to be switched now in 
%$\alpha_1$ and $\alpha_2$ with the quantile definition for $z_{\alpha}$ -- 
%please check.} 
%\mc{yes they had to be switched}

\paragraph{Bias-Corrected and Accelerated (BCA) CI}
The BCA CI was first suggested in \citet{efron1987better}. Let $Z_{(i)}$ be the 
original sample without the $i$th block $z_i$ for $i \in \{1, \ldots, k\}$, let 
$\hat{\theta}_{(i)}$ be the statistic of $Z_{(i)}$, and let 
$\hat{\theta}_{(.)} = k^{-1}\sum_{i=1}^{k} \hat{\theta}_{(i)}$. 
Let
\begin{equation*}
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}.
\end{equation*}
Define
\begin{equation*}
\alpha_1 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{\alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{\alpha/2})}\right)
\end{equation*}
and
\begin{equation*}
\alpha_2 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{1 - \alpha/2})}\right).
\end{equation*}
%\eds{please check $z_{\alpha/2}$ and $z_{1 - \alpha/2}$ in 
%$\alpha_1$ and $\alpha_2$ with the quantile definition for $z_{\alpha}$} 
%\mc{this one is okay}
A $(1 - \alpha)100\%$ ~BCA CI is
\[
(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
\]
This CI is not necessarily centered by $\hat\theta_n$. The BCA method corrects 
for bias and skewness of the $B$ bootstrap point estimates 
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including 
bias-correction and acceleration factors. The acceleration factor refers to the 
rate of change of the standard error of $\hat\theta_n$ with respect to $\theta$.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_sigma}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal standard deviation $\sigma_w$ %\eds{$\sigma_w$?} \mc{addressed}
    of a stationary series with 
    marginal unit exponential distribution obtained by transforming an AR(1) process
    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_sigma}
\end{figure}

@@

The empirical coverage rates for $\mu$, $\sigma_w$, %\eds{define $\sigma_w$} 
%\mc{added definitions for $\mu$ and $\sigma_w$ in the above paragraph} 
and 
the lag-1 autocorrelation coefficient, %\mc{replaced $\phi$ here, as I understand
%it, we are not using $\phi$ in reference to the temporal dependence of the 
%exponentially distributed series?}, 
as well as 95\%
confidence intervals of the real coverage are displayed in 
\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_phi}}. 
Additionally, a set of 50 CIs are displayed for each of the percentile, 
BC, and recentered percentile approaches for exponentially distributed
samples of $n \in \{800, 1600\}$ with lag-1 autocorrelation coefficient 0.355
($\phi = 0.4$) in Figure~\ref{fig:eri}.

It appears that a greater sample size is generally required for the bootstrap
CIs to cover the mean and standard deviation parameters in the exponential
margin case than in the normal margin case. However, the trends and patterns
discussed in the main text regarding the performance of various methods and
diverse parameters remain consistent. For example, Student's $t$ confidence
intervals still exhibit higher coverage rates in comparison to alternative
methods. Performance continues to be more favorable when temporal dependence is
negative rather than positive. Of particular significance, the percentile, BC,
and BCA confidence intervals still display a decline in coverage accuracy for
the lag-1 autocorrelation coefficient as sample size increases as demonstrated
in Figure~\ref{fig:eri}. Both the percentile and BC intervals persist in
manifesting the same bias issue. On the other hand, the recentered percentile
confidence interval continues to be effective in estimating the temporal 
dependence %\mc{replaced $\phi$ again here} 
due to the
inherent unbiasedness of the original point estimator. In sum, the findings for
series that are marginally exponentially distributed closely mirror those
attained for series that are marginally normally distributed.
